%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sanwal}{Hussain}{ \urlstyle{same}\href{http://sanwalhussain.com}{sanwalhussain.com }| Al Iskan, Riyadh, Saudi Arabia\\
\href{mailto:meetsanwal@gmail.com}{meetsanwal@gmail.com} | +966 58 061 2728
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{FEDERAL University}
\descript{BS in Electrical Engineering}
\location{Aug 2016 | Islamabad, Pakistan}
College of Engineering \\
\location{ Cum. GPA: 3.15 / 4.0 \\
Major GPA: 3.92 / 4.0}
\sectionsep

\subsection{Murray College}
\descript{F.Sc. Pre-Engineering}
\location{Jan 2012 | Sialkot, Pakistan}
\sectionsep

\subsection{Cathedral High School}
\location{Aug 2009 |  Sialkot, Pakistan}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook.com/esanwalz}{\bf esanwalz} \\
Github:// \href{https://github.com/sanwalhussain}{\bf sanwalhussain} \\
LinkedIn://  \href{https://www.linkedin.com/in/sanwalhussain}{\bf sanwalhussain} \\
Twitter://  \href{https://twitter.com/meetsanwal}{\bf @meetsanwal} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Online}
Cloud Computing \\
Data Analytics  \\
Technical SEO \\
Blockchain Smart Contracts \\
Machine Learning \\
Web3 Basic
\sectionsep

\subsection{Undergraduate}
Industrial Electronic \\
Control Systems \\
Communications systems \\
OOP and Data Structures \\
Circuit and Electronics \\
Signals and Systems\\
Engineering Drawing and Analysis \\
Computer Networks and Architecture \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

Problem Solving \textbullet{}   Critical Thinking \\ Communication\textbullet{} Business Planning \\
\subsection{Programming}
\location{Over 1000 lines:}
Java \textbullet{}   Vue.js \textbullet{} Python \textbullet{} Javascript \\
PHP \textbullet{} Matlab \\ 
\location{Familiar:}
Google Cloud \textbullet{} AWS \textbullet{} Tableau \\
Odoo  \textbullet{} SAP \textbullet{} Maximo 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Fair Deal Trading Compnay}
\descript{| Sales Engineer }
\location{March 2020 - Present | Riyadh, Saudi Arabia}
\sectionsep

\runsubsection{OGDCL}
\descript{| Instrumentation Engineer at Dakhni Gas Processing Plant and Oil Field }
\location{Aug 2019 – Dec 2019 | Jand, Pakistan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Complete work orders and provide maintenance support on automated production equipment.
\item Calibration, testing, and trouble-shooting of control valves and other valve-related instruments.
\item Testing and calibration of all type of process transmitters (Ft, Lt, Pt, Tt) using modern systems communicating via the HART® protocol.
\end{tightemize}
\sectionsep

\runsubsection{Hydro Tech Pak (Pvt) Ltd}
\descript{| Assistant Shift Engineer }
\location{Dec 2018 – July 2019 | Sialkot, Pakistan}
\begin{tightemize}
\item Operate and maintain the plant during the shift according to company policies and procedures.
\item Work with the maintenance team to ascertain the condition of equipment's, required maintenance activities, and scheduled overhauls.
\item Ensuring the standards are being followed for all tasks done.
\end{tightemize}
\sectionsep

\runsubsection{Crown Foam Industries}
\descript{| Assistant C\&I Engineer}
\location{May 2017 – Nov 2018 | Sialkot, Pakistan}
\begin{tightemize}
\item Implement daily electrical and instrument inspection and records.
\item Troubleshooting of automated machinery and programmed PLC, VFD \& HMI.
\item Align, adjust and calibrate systems and equipment according to specifications and to maintain records of repairs, calibrations and tests.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{FUUAST Electrical Lab}
\descript{| Head Undergraduate Researcher}
\location{Mar 2015 – May 2016 | Islamabad, Pakistan}
Led the development of \textbf{Gesture Controlled Wheelchair}, The First Ever Breakthrough GESTURE Control Wheelchair Using LEAP Motion and Home Automation. A revolutionary new invention that can be controlled with just your hands.
\sectionsep

\section{Professional Association}
\runsubsection{Pakistan Engineering Council}
\descript{| Registered Engineer}
\location{PEC NO: ELECT/58486}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2016	     & Top 50/1167  & National ICT R\&D Fund (Ministry of IT)\\
2015	     & 2\textsuperscript{nd}  & Institute of Space Technology (IST)\\
2015	     & National  & IIUI FETEX Robotic Competition Finalist\\
2015	     & National  & FAST NASCON '15 Finalist\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}  \documentclass[]{article}
